---
title: "Coefficient plots"
date: '2019 10 2 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### source[data screencast by david robinson] (https://github.com/dgrtwo/data-screencasts)
### source[M25. Many models] (https://r4ds.had.co.nz/many-models.html)
### selected data from tidy tuesday to explore coefficient plots based on live data screencast run by david robinson. It is applied to 8 data as below. 
```{r}
library(tidyverse)
library(broom)
library(scales)

plot_theme <- 
  theme(axis.title = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none",
        plot.title = element_text(size = 14, margin = margin(b = 10)),
        plot.subtitle = element_text(size = 11, color = "darkslategrey", margin = margin(b = 25)),
        plot.caption = element_text(size = 9, margin = margin(t = 10), color = "#757575", hjust = 1))
```
#### source[Tidy Tuesday Screencast: analyzing college major & income data in R by david robinson] (https://www.youtube.com/watch?v=nx5yhXAQLxw&t=3668s)
```{r 1. College major income}
recent_grads <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-16/recent-grads.csv") %>% 
  mutate(Major = str_to_title(Major),
         Major = fct_reorder(Major, Median))

model <- recent_grads %>% 
  lm(Median ~ Major_category, data = ., weights = Sample_size) %>% 
  summary()
```

```{r}
major_category <- recent_grads %>% 
  select(Major, Major_category, Total, ShareWomen, Sample_size, Median) %>% 
  add_count(Major_category) %>% 
  filter(n >= 10) %>% 
  nest(-Major_category) %>% 
  mutate(model = map(data, ~t.test(.$Median)),
         tidied = map(model, tidy)) %>% 
  unnest(tidied) %>% 
  mutate(Major_category = fct_reorder(Major_category, estimate)) %>% 
  ggplot(aes(estimate, Major_category)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low,
                     xmax = conf.high)) +
  scale_x_continuous(labels = dollar_format()) +
  labs(x = "estimate",
       y = "",
       title = "Average income by major category in USA",
       subtitle = "Education and Humanites & Liberal Arts show comparably lower average income, which \nstand higher women shares over major categories.",
       caption = "source | fivethirtyeight/ACS") +
  theme_minimal() +
  plot_theme
```
### source [Tidy Tuesday Screencast: analyzing Maryland bridges with R by david robinson] (https://www.youtube.com/watch?v=kzM-4jMh9Qs&t=3491s)
```{r 2. Baltimore bridges}
baltimore_bridges <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-27/baltimore_bridges.csv") %>%
  select(-vehicles) %>%
  mutate(inspection_yr = inspection_yr + 2000,
         decade = 10 * (yr_built %/% 10),
         responsibility = fct_lump(responsibility, 4),
         county = str_to_title(county))
```

```{r}

bridges <- baltimore_bridges %>%
  mutate(responsibility = fct_relevel(fct_lump(responsibility, 4), "Other"),
       owner = fct_relevel(fct_lump(owner, 4), "Other"),
       county = fct_relevel(fct_lump(county, 4), "Other"))
 
bridges %>% 
  mutate(good = bridge_condition == "Good") %>% 
  lm(good ~responsibility + owner + county , data = .) %>%
  tidy(conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  extract(term, c("category", "term"), "^([a-z]+)([A-Z].*)") %>%
  mutate(term = fct_reorder(term, estimate)) %>%
  ggplot(aes(estimate, term, color = category)) +
  geom_point(show.legend = FALSE) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high)) +
  geom_vline(lty = 2, xintercept = 0) +
  scale_color_brewer(palette = "Set2") +
  facet_wrap(~ category, ncol = 1, scales = "free_y") +
  labs(x = "Estimated effect on Baltimore bridges",
       y = "",
       title = "Features relating to the condition of Baltimore bridges",
       caption =  "source | Federal Highway Administration") +
  theme_minimal() + 
  plot_theme
 
```

```{r}
library(splines)


model <- bridges %>%
  mutate(good = bridge_condition == "Good") %>%
  glm(good ~ ns(yr_built, 4) + responsibility + county, 
      data = ., family = "binomial")


model %>%
  tidy(conf.int = TRUE) %>%
 # filter(str_detect(term, "responsibility|county")) %>%
  mutate(term = str_replace(term, "responsibility", "Responsibility: "),
         term = str_replace(term, "county", "County: "),
         term = fct_reorder(term, estimate)) %>% 
  ggplot(aes(estimate, term)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                 na.rm = TRUE) +
  geom_vline(xintercept = 0, color = "#9a2543", lty = 2) +
  labs(x = "estimate(the higher the better)",
       y = "",
       title = "Features affecting conditions of Baltimore bridges",
       subtitle = "It is more likely to be affected by built year rather than parts \nsuch as county or responsibility",
       caption = "source | Federal Highway Administration") +
  theme_minimal() +
  plot_theme
```
```{r}
bridges_yr <- baltimore_bridges %>%
  filter(yr_built >= 1900)


library(splines)

simple_model <- bridges_yr %>%
  mutate(good = bridge_condition == "Good") %>%
  glm(good ~ ns(yr_built, 4), data = ., family = "binomial")

model <- bridges_yr %>%
  mutate(good = bridge_condition == "Good") %>%
  glm(good ~ ns(yr_built, 4) + responsibility + county, data = ., family = "binomial")

augment(simple_model, bridges_yr, type.predict = "response") %>%
  ggplot(aes(yr_built, .fitted)) +
  geom_line() +
  expand_limits(y = 0) +
  scale_y_continuous(labels = percent_format()) +
  labs(title = "Predicted probability a bridge is rated 'Good'") +
  theme_minimal() +
  plot_theme
```


```{r}
augment(model, bridges_yr, type.predict = "response") %>%
  ggplot(aes(yr_built, .fitted, color = responsibility)) +
  geom_line() +
  expand_limits(y = 0) +
  facet_wrap(~ county) +
  scale_y_continuous(labels = percent_format()) +
  labs(title = "Predicted probability a bridge is rated 'Good'") +
  theme_minimal() +
  theme(axis.title = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 16, margin = margin(b = 10)),
        plot.subtitle = element_text(size = 11, color = "darkslategrey", margin = margin(b = 25)),
        plot.caption = element_text(size = 9, margin = margin(t = 10), color = "#757575", hjust = 1))

augment(model, bridges_yr, type.predict = "response") %>%
  mutate(owner = fct_relevel(fct_lump(owner, 4)))  %>% 
  ggplot(aes(yr_built, .fitted, color = owner)) +
  geom_line() +
  expand_limits(y = 0) +
  facet_wrap(~ county) +
  scale_y_continuous(labels = percent_format()) +
  labs(title = "Predicted probability a bridge is rated 'Good'") +
  theme_minimal() +
  theme(axis.title = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 16, margin = margin(b = 10)),
        plot.subtitle = element_text(size = 11, color = "darkslategrey", margin = margin(b = 25)),
        plot.caption = element_text(size = 9, margin = margin(t = 10), color = "#757575", hjust = 1))
```
```{r}
model %>%
  tidy(conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  extract(term, c("category", "term"), "^([a-z]+)([A-Z].*)") %>%
  mutate(term = fct_reorder(term, estimate)) %>%
  drop_na() %>% 
  ggplot(aes(estimate, term, color = category)) +
  geom_point(na.rm = TRUE) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                 na.rm = TRUE) +
  geom_vline(lty = 2, color = "#9a2543", xintercept = 0) +
  scale_color_brewer(palette = "Set2") +
  facet_wrap(~ category, ncol = 1, scales = "free_y") +
  labs(x = "Estimated effect on Baltimore bridges",
       y = "",
       title = "Features relating to the condition of Baltimore bridges",
       caption =  "source | Federal Highway Administration") +
  theme_minimal() + 
  plot_theme
```
### source[Tidy Tuesday: Analyzing dolphin data in R by david robinson by david robinson] (https://www.youtube.com/watch?v=KiqpX-gNIS4)
```{r 3.Cetacean}
cetaceans_raw <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-12-18/allCetaceanData.csv")

cetaceans <- cetaceans_raw %>%
  select(-X1) %>%
  mutate(birthYear = as.integer(birthYear),
         age = if_else(status == "Died", year(statusDate) - birthYear, NA_real_))
```

```{r}
acquisition_model <- cetaceans %>%
  mutate(alive = status == "Alive") %>%
  filter(acquisition != "Unknown") %>% 
  lm(alive ~ acquisition, data = .)

acquisition_model %>%
  tidy(conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  arrange(desc(estimate)) %>%
  extract(term, c("category", "term"), "^([a-z]+)([A-Z].*)") %>%
  mutate(term = reorder(term, estimate)) %>%
  ggplot(aes(estimate, term)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high)) +
  labs(caption = "source | The Pudding") +
  theme_minimal() +
  plot_theme
```

```{r}
library(survival)

dolphin_survival <- cetaceans %>%
  filter(status %in% c("Alive", "Died")) %>%
  mutate(deathYear = ifelse(status == "Alive", 2017, year(statusDate)),
         status = ifelse(status == "Alive", 0, 1),
         age = deathYear - birthYear) %>%
  filter(!is.na(deathYear)) %>%
  select(birthYear, deathYear, status, sex, age, acquisition, species) %>%
  filter(deathYear >= birthYear) %>%
  filter(sex != "U")

model <- survfit(Surv(age, status) ~ sex, dolphin_survival)

tidy(model) %>%
  ggplot(aes(time, estimate, color = strata)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  scale_y_continuous(labels = percent_format()) +
  labs(y = "Estimated % survival")

coxph(Surv(age, status) ~ sex, dolphin_survival) %>%
  tidy()
```

```{r}
model <- survfit(Surv(age, status) ~ acquisition, dolphin_survival)

tidy(model) %>%
  filter(strata != "acquisition=Unknown") %>%
  ggplot(aes(time, estimate, color = strata)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "",
       y = "Estimated % survival",
       caption = "source | The Pudding")+
  theme_minimal() +
  theme(axis.title = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(size = 16, margin = margin(b = 10)),
        plot.subtitle = element_text(size = 11, color = "darkslategrey", margin = margin(b = 25)),
        plot.caption = element_text(size = 9, margin = margin(t = 10), color = "#757575", hjust = 1))
```
### source[Tidy Tuesday screencast: analyzing board games and predicting ratings in R] (https://www.youtube.com/watch?v=qirKGdQvy9U)
```{r 4.Board games}
board_games <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-12/board_games.csv") %>% 
  mutate(decade = 10 * (year_published %/% 10))
```

```{r}
categorical_variables <- board_games %>% 
  select(game_id, name, family, category, artist, designer, mechanic) %>% 
  gather(type, value, -game_id, -name) %>% 
  filter(!is.na(value)) %>% 
  separate_rows(value, sep = ",") %>% 
  arrange(game_id)

categorical_count <- categorical_variables %>% 
  count(type, value, sort = TRUE)
```

```{r}
library(drlib)
categorical_count %>% 
  group_by(type) %>% 
  top_n(10, n) %>% 
  ungroup() %>% 
  mutate(value = reorder_within(value, n, type),
         type = fct_reorder(type, n, .desc = TRUE)) %>% 
  ggplot(aes(value, n, fill = type)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ type,
             scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Most common categories") +
  theme_minimal()
```

```{r}
lm(average_rating ~ 
     log2(max_players + 1) +
     log2(max_playtime + 1) +
     year_published,
   board_games) %>% 
  tidy()
```

```{r}
non_categorical_variables <- board_games %>% 
  transmute(game_id,
            name,
            year = year_published - 1950,
            log2_max_players = log2(max_players + 1),
            log2_max_playtime = log2(max_playtime + 1)) %>% 
  gather(feature, value, -game_id, -name)


features <- categorical_variables %>% 
  unite(feature, type, value, sep = ":") %>% 
  add_count(feature) %>% 
  filter(n >= 20) %>% 
  mutate(value = 1) %>% 
  bind_rows(non_categorical_variables)

```
```{r}
library(glmnet)
library(Matrix)
library(tidytext)

feature_matrix <- features %>%
  cast_sparse(game_id, feature, value)

ratings <- board_games$average_rating[match(rownames(feature_matrix),
                                            board_games$game_id)]

cv_lasso <- cv.glmnet(feature_matrix, ratings)

plot(cv_lasso)
```

```{r}
cv_lasso$glmnet.fit %>% 
  tidy() %>% 
  filter(lambda == cv_lasso$lambda.1se) %>% 
  arrange(desc(estimate)) %>% 
  filter(term != "(Intercept)") %>% 
  top_n(25, abs(estimate)) %>% 
  mutate(term = fct_reorder(term, estimate)) %>% 
  ggplot(aes(term, estimate)) +
  geom_col(aes(fill = if_else(estimate >= 0, "#73e2cd", "#e1ca6d"))) +
  scale_fill_identity()+
  coord_flip() +
  labs(x = "",
       y = "Coefficient",
       title = "Features based on coefficients",
       subtitle = "Features: category, family, artist, designer, mechanic based on a LASSO regression",
       
       caption = "source | Board Game Geeks") +
  theme_minimal() +
  theme_plot()
```
### source[Tidy Tuesday screencast: scraping and analyzing ramen reviews in R by david robinson] (https://www.youtube.com/watch?v=tCa2di7aEP4&t=963s)
```{r 5.Ramen ratings}
ramen_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv") %>% 
  mutate(style = fct_relevel(fct_lump(style, 4), "Pack"),
         country = fct_relevel(fct_lump(country, 12), "Other"),
         brand = fct_relevel(fct_lump(brand, 20), "Other"))%>%
  replace_na(list(style = "Other")) 

lm(stars ~ brand + country + style, ramen_ratings) %>%
  tidy(conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  arrange(desc(estimate)) %>%
  extract(term, c("category", "term"), "^([a-z]+)([A-Z].*)") %>%
  mutate(term = fct_reorder(term, estimate)) %>%
  ggplot(aes(estimate, term, color = category)) +
  geom_point(show.legend = FALSE) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high)) +
  geom_vline(lty = 2, color = "#9a2543", xintercept = 0) +
  facet_wrap(~ category, ncol = 1, scales = "free_y") +
  scale_color_brewer(palette = "Set2") +
  labs(x = "Estimate",
       y = "",
       title = "Features of ramen ratings based on coefficients",
       cation = "source | TheRamenRater.com") +
  theme_minimal() +
  plot_theme
```
### source[Tidy Tuesday screencast: predicting wine ratings by david robinson] (https://www.youtube.com/watch?v=AQzZNIyjyWM&t=1757s)
```{r 6.Wine ratings}
wine_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-28/winemag-data-130k-v2.csv") %>%
  select(-X1) %>%
  extract(title, "year", "(20\\d\\d)", 
          convert = TRUE, 
          remove = FALSE) %>%
  mutate(year = ifelse(year < 1900, NA, year)) %>%
  filter(!is.na(price))
```

```{r}
model <- wine_ratings %>% 
  replace_na(list(taster_name = "Missing",
                  country = "Missing")) %>% 
  mutate(country = fct_relevel(fct_lump(country, 7), "US"),
         taster_name = fct_relevel(fct_lump(taster_name, 6), "Missing")) %>% 
  lm(points ~ log2(price) + country + year + taster_name,
     data =.)

model %>% 
  tidy(conf.int = TRUE) %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = str_replace(term, "country", "Country: "),
         term = str_replace(term, "taster_name", "Taster: "),
         term = fct_reorder(term, estimate)) %>% 
  ggplot(aes(estimate, term)) +
  geom_point(aes(color = if_else(estimate >= 0, "#780303",
                                     "#e1ca6d"))) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high,
                     color = if_else(estimate >= 0, "#780303",
                                     "#e1ca6d"))) +
  geom_vline(lty = 2, color = "#9a2543", xintercept = 0) +
  scale_color_identity() +
  labs(x = "estimate",
       y = "",
       title = "Features of wine ratings based on coefficients",
       subtitle = "price and country are estimated to relate to the average rating of wine",
       caption = "source | Kaggle") +
  theme_minimal() +
  plot_theme
  
# Lasso regression on words in description with tidytext package 
```
###source [Tidy Tuesday screencast: analyzing NYC restaurant inspections with R by david robinson] (https://www.youtube.com/watch?v=em4FXPf4H-Y&t=2364s)
```{r 7.NYC restaurants inspection}
library(lubridate)

restaurant_inspections_raw <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-12-11/nyc_restaurants.csv") 

restaurant_inspections <- restaurant_inspections_raw %>% 
  janitor::clean_names() %>%
  select(-zipcode, -violation_code) %>%
  mutate(inspection_date = mdy(inspection_date)) %>%
  separate(inspection_type, c("inspection_program",
                              "inspection_type"), sep = " / ")  
  
```

```{r}
inspections <- restaurant_inspections %>%
  group_by(camis,
           dba,
           boro,
           cuisine = cuisine_description,
           inspection_date,
           action,
           score,
           grade,
           inspection_type,
           inspection_program) %>% 
   filter(inspection_program == "Cycle Inspection",
          inspection_type == "Initial Inspection") %>%
  arrange(desc(inspection_date)) %>%
  distinct(camis, .keep_all = TRUE) %>% 
  group_by(dba, cuisine) %>%
  summarize(locations = n(),
            avg_score = mean(score),
            median_score = median(score)) %>%
  ungroup() %>%
  arrange(desc(locations))

cuisine <- inspections %>% 
  add_count(cuisine) %>% 
  filter(n >= 200) %>% 
  nest(-cuisine) %>%
  mutate(model = map(data, ~ t.test(.$avg_score)),
         tidied = map(model, tidy)) %>% 
  unnest(tidied) %>% 
  mutate(cuisine = str_remove(cuisine, " \\(.*"),
         cuisine = fct_reorder(cuisine, estimate)) %>%
  ggplot(aes(estimate, cuisine)) +
  geom_point(aes(color = if_else(cuisine == "Indian", 
                                 "firebrick3", "black"))) +
  geom_errorbarh(aes(xmin = conf.low,
                     xmax = conf.high,
                     color = if_else(cuisine == "Indian", "firebrick3", "black"))) +
  geom_vline(lty = 2, color = "firebrick3", xintercept = 19.6) +
  scale_color_identity() +
  labs(x = "Average inspection score of violation ",
       y = "",
       title = "Average violation inspection by cuisine in New York City",
       caption = "source | NYC OpenData/NYC Health Department") +
  theme_minimal() +
  plot_theme
  
```
### source[Tidy Tuesday screecast: analyzing pizza ratings by david robinson] (https://www.youtube.com/watch?v=Mkac8DHScps&t=52s)
```{r 8.NYC pizza places}
pizza_jared <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_jared.csv")
```

```{r}
answer_orders <- c("Never Again", "Poor", "Average", "Good", "Excellent")

by_place_answer <- pizza_jared %>% 
  mutate(time = as.POSIXct(time, origin = "1970-01-01"),
         date = as.Date(time),
         answer = fct_relevel(answer, answer_orders)) %>% 
  group_by(place, answer) %>% 
  summarize(votes = sum(votes)) %>% 
  mutate(total = sum(votes),
         percent = votes / total,
         answer_integer = as.integer(answer),
         average = sum(answer_integer * percent)) %>% 
  ungroup()

```

```{r}
t_test_repeated <- function(x, frequency) {
  tidy(t.test(rep(x, frequency)))
}

by_place_answer %>% 
  filter(total >=3) %>% 
  group_by(place, total) %>% 
  summarize(t_test_result = list(t_test_repeated(answer_integer, votes))) %>% 
  ungroup() %>% 
  unnest(t_test_result) %>% 
  select(place, total, 
         average = estimate,
         low = conf.low,
         high = conf.high) %>% 
  top_n(16, total) %>% 
  mutate(place = glue::glue("{ place } ({ total })"),
         place = fct_reorder(place, average)) %>% 
  ggplot(aes(average, place)) +
  geom_point(aes(size = total, color = if_else(average >= 3.6, "#ffcc00", "#998d7d"))) +
  geom_errorbarh(aes(xmin = low, xmax = high,
                     color = if_else(average >= 3.6, "#ffcc00", "#998d7d"))) +
  geom_vline(lty = 2, size = 0.7, 
             xintercept = 3.6,,
             color = "#0e47d3") +
  scale_color_identity() +
  labs(x = "Average score (Likert Scale:1-5)",
       y = "",
       title = "Best pizza places in NYC",
       subtitle = "Pizza places with above/below average in New York city. (#) stands \nnumber of repondents in votes.It is not likely to affect rating the quality \nof pizza directly.",
       caption  = "source | Jared Lander & Ludmila Janda, Tyler Richards, DataFiniti") +
  theme_minimal() +
  plot_theme

```
