---
title: "Nobel Prize Winners"
author: "sung inkyung"
date: "2019 5 27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(ggalluvial)
library(LaCroixColoR)
library(cowplot)
```
### source: datascreencast by david robinson:https://github.com/dgrtwo/data-screencasts/blob/master/nobel-prize.Rmd,                         Tidy Tuesday Screencast: Analyzing Thanksgiving dinners in R:https://www.youtube.com/watch?v=yWSpLfmES7w&t=2871s
```{r}
nobel_winners <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-14/nobel_winners.csv") %>% 
  distinct(full_name, prize_year, category, .keep_all = TRUE) %>% 
  mutate(decade = 10 * (prize_year %/% 10),
         age = prize_year - year(birth_date))

nobel_winner_all_pubs <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-14/nobel_winner_all_pubs.csv") %>% 
  mutate(prize_decade = 10 * (prize_year %/% 10))
```

```{r}
glimpse(nobel_winners)

glimpse(nobel_winner_all_pubs)
```

```{r}
skimr::skim(nobel_winners)

skimr::skim(nobel_winner_all_pubs)
```

```{r}
nobel_winners %>% 
  count(category, sort = TRUE)
```

```{r}
plot.category <- nobel_winners %>% 
  count(category,
        decade = 10 * (prize_year %/% 10), sort = TRUE) %>% 
  ggplot(aes(decade, n, fill = category)) +
  geom_col()+
  scale_fill_manual(values = lacroix_palette("PeachPear", n = 6, type = "discrete"))+
  theme_half_open()

plot.category

plot.gender <- nobel_winners %>%
  count(decade,
        category,
        gender = coalesce(gender, laureate_type)) %>%
  group_by(decade, category) %>%
  mutate(percent = n / sum(n)) %>%
    ggplot(aes(decade, percent)) +
  geom_point(aes(color = gender))+
  theme_half_open()

plot.gender
```

```{r}
plot_grid(plot.category, plot.gender, 
          labels = c("A", "B"),
          nrow = 2, align = "v")
```

```{r}
# alluvial diagram application (to be done: simplify decade division like seq(1900, 2010, by=50))
p <- nobel_winners %>% 
  group_by(category, decade, gender, birth_country) %>% 
  filter(gender != "NA") %>% 
  summarise(winners = n(),
            winners_per_year = winners / n_distinct(prize_year)) %>% 
  ungroup() %>% 
  ggplot(aes(axis1 = category, axis2 = gender, axis3 = decade, y = winners))+
  geom_alluvium(aes(fill = category)) +
  geom_stratum(fill = "gray70", size = 0.1, width = 0.4) +
  geom_text(stat = "stratum", color = "grey20", size = 3, label.strata = T)+
  scale_x_discrete(limits = c("Category", "Gender", "Decade"), 
                   expand = c(0, 0), 
                   position = "top")+
  scale_y_discrete()+
  scale_fill_manual(values = lacroix_palette("PeachPear", n = 6, type = "discrete"))+
  theme(axis.title.x = element_text(size = 11),
          axis.title.y = element_text(size = 11),
          axis.text.x = element_text(size = 10, color = "black", face = "bold"),
          axis.text.y = element_text(size = 10),
          legend.position = "bottom",
          legend.key.width = unit(6, "lines"),
          legend.key.height = unit(0.75, "lines"),
          legend.spacing.x = unit(0.5, 'cm'),
          legend.title = element_text(size = 10, face = "bold"),
          legend.text = element_text(size = 9)) +
    guides(fill = guide_legend(title.position = "top", 
                               title.hjust = .5, 
                               label.position = "bottom")) +
    labs(x = NULL, y = "Nobel Prize Gender Proportion")
```

```{r}
nobel_winners %>% 
  mutate(category = fct_reorder(category, age, median, na.rm = TRUE)) %>% 
  ggplot(aes(category, age)) +
  geom_boxplot() +
  geom_jitter(size = .7, alpha =.5) +
  geom_hline(yintercept =  59.5, color = "#8d1673", linetype = "dashed", size = .9)+
  coord_flip()

nobel_winners %>% 
  mutate(category = fct_reorder(category, age, median, na.rm = TRUE)) %>% 
  ggplot(aes(category, age, fill = category, alpha = .7)) +
  geom_violin() +
  geom_jitter(size = .7, alpha =.5) +
  geom_hline(yintercept =  59.5, color = "#8d1673", lty = "dashed", size = .9)+
  scale_fill_manual(values = lacroix_palette("PeachPear", n = 6, type = "discrete"))+
  coord_flip()+
  theme_half_open()
```

```{r}
p <- nobel_winners %>% 
    distinct(full_name, prize_year, category, .keep_all = TRUE) %>% 
    mutate(decade = 10 * (prize_year %/% 10),
           age = prize_year - year(birth_date),
           year = prize_year) %>% 
  ggplot(aes(year, age))+ 
  geom_point(size = 3, alpha = .5, color = "black")+
  geom_smooth(aes(fill = "#8d1673")) +
  scale_x_continuous() +
  scale_y_continuous() +
  theme(legend.position = "none") +
  labs(title = "Nobel Prize age distribution over time")
```
### source: plotly package by Carson Sievert (https://plotly-r.com/overview.html)
```{r}
library(plotly)

p <- nobel_winners %>% 
    distinct(full_name, prize_year, category, .keep_all = TRUE) %>% 
    mutate(decade = 10 * (prize_year %/% 10),
           age = prize_year - year(birth_date),
           year = prize_year) %>% 
  ggplot(aes(year, age))+ 
  geom_point(alpha = .7)+
  geom_smooth(aes(color = category, 
                  fill = category)) +
  geom_hline(yintercept = 59.45, 
             lty = "dotted", 
             size = .7, 
             color = "#8d1673") +
  scale_fill_manual(values = lacroix_palette("PeachPear", n = 6, type = "discrete"))+
  facet_wrap(~category)+
  theme_half_open()

ggplotly(p)
```
### source: gghighlight (https://yutani.rbind.io/post/2017-10-06-gghighlight/)
```{r}
library(gghighlight)

p <- nobel_winners %>% 
  group_by(decade, category) %>% 
  count(decade,
        category) %>% 
  mutate(percent = n / sum(n)) %>% 
  ungroup() %>% 
  ggplot(aes(decade, n)) +
  geom_col() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  gghighlight(category == "Economics") +
  theme_half_open()
```

```{r}
p <- nobel_winners %>% 
  group_by(decade, category) %>% 
  count(decade,
        category) %>% 
  mutate(percent = n / sum(n)) %>% 
  ungroup() %>% 
  ggplot(aes(decade, n, fill = category)) +
  geom_col() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = lacroix_palette("PeachPear", n = 6, type = "discrete"))+
  gghighlight() +
  theme_half_open() +
  facet_wrap(~category) +
  labs(title = "Nobel Prize category distribution over time")
```

```{r}
p <- nobel_winners %>% 
  group_by(decade, category) %>% 
  count(decade,
        category,
        gender= coalesce(gender, laureate_type)) %>% 
  mutate(percent = n / sum(n)) %>% 
  ungroup() %>% 
  ggplot(aes(decade, n, fill = gender)) +
  geom_col() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_manual(values = c("#ff73c1", "#0096b7", "#f7c56e"))+
  gghighlight() +
  theme_half_open()+
  facet_wrap(~category)+
  labs(title = "Nobel Prize gender distribution over time")
```
### sources: DATA VISUALIZATION BY KIERAN HEALY (https://socviz.co/refineplots.html#use-theme-elements-in-a-substantive-way),                 UC Business Analytics R Programming Guide (http://uc-r.github.io/gda)
```{r}
library(ggridges)

nobel_winners %>% 
    count(decade,
          category,
          gender = coalesce(gender, laureate_type)) %>% 
  group_by(decade, category) %>% 
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(decade, category, 
             color = gender, 
             fill = gender,
             alpha = .7)) +
  ggridges::geom_density_ridges(scale = .95, 
                                rel_min_height = 0.01, 
                                gradient_lwd = 1.) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_fill_manual(values = c("#ff73c1", "#0096b7", "#f7c56e"), 
                    labels = c("female", "male", "orgranization")) +
  scale_color_manual(values = c("#ff73c1", "#0096b7", "#f7c56e"), 
                     guide = "none") +
  theme_ridges(font_size = 13, 
               grid = TRUE)+
  theme(axis.title.y = element_blank()) +
  guides(fill = guide_legend(
    override.aes = list(
    fill = c("#ff73c1", "#0096b7", "#f7c56e"),
    color = NA, point_color = NA)))+
  ggtitle("Nobel prize gender distribution per category since 1900") +
  theme_ridges(center = TRUE) 
```

```{r}
nobel_winners %>% 
  count(decade,
        category,
        gender = coalesce(gender, laureate_type)) %>%  
  mutate(percent = n / sum(n)) %>% 
  ggplot(aes(decade, n, fill = category)) +
  geom_col() +
  facet_grid(gender~category) +
  scale_fill_manual(values = lacroix_palette("PeachPear", n = 6, type = "discrete")) +
  theme_half_open() +
  labs(x = "decade",
       Y = "# of Nobel prize winners",
       title = "Nobel prize categroy and gender distribution over time")
    
```

```{r}
nobel_winners%>% filter(category == "Economics", gender == "Female")

nobel_winners %>% 
  filter(category%in% c("Economics", "Physics"), gender == "Female")
```

```{r}
nobel_winners %>% 
  count(birth_country = fct_lump(birth_country, 15), sort = TRUE)

nobel_winners %>% 
  count(birth_country = fct_lump(birth_country, 9), sort = TRUE)

nobel_winners %>% 
  count(prize_share)

nobel_winners %>% 
  count(full_name, sort = TRUE)
```

```{r}
nobel_winners %>% 
  add_count(full_name) %>% 
  arrange(desc(n)) %>% 
  select(prize_year, category, full_name) 

nobel_winners %>% 
  filter(category == "Medicine", full_name == "Jack W.Szostak") %>% 
  View()
```

```{r}
nobel_winners %>% 
  distinct(full_name, prize_year, category) %>% 
  group_by(full_name) %>% 
  mutate(prizes = n(),
         distinct_prizes = n_distinct(category)) %>% 
  arrange(desc(prizes), full_name) %>%
  View()
```


```{r}
nobel_winners %>% 
  filter(!is.na(birth_country)) %>% 
  count(birth_country = fct_lump(birth_country, 9), 
        category, sort = TRUE) %>% 
  mutate(birth_country = fct_reorder(birth_country, n)) %>% 
  ggplot(aes(birth_country, n, fill = category)) +
  geom_col() +
  guides(fill = guide_legend(reverse = TRUE)) +
  coord_flip() +
  scale_fill_manual(values = lacroix_palette("PeachPear", n = 6, type = "discrete")) +
  theme_half_open()
```

```{r}
nobel_winners %>% 
  filter(!is.na(birth_country)) %>% 
  count(birth_country = fct_lump(birth_country, 9), 
        category, sort = TRUE) %>% 
  mutate(birth_country = fct_reorder(birth_country, n)) %>% 
  ggplot(aes(birth_country, n, fill = category)) +
  geom_col() +
  facet_wrap(~category) +
  coord_flip() +
  scale_fill_manual(values = lacroix_palette("PeachPear", n = 6, type = "discrete")) +
  theme_half_open() +
  labs(title = "Nobel prize category distribution per country")
```

```{r}
# radar chart application

nobel_winners %>% 
  count(category,
        decade = 10 * (prize_year %/% 10), 
        birth_country = fct_lump(birth_country, 11), 
        category, sort = TRUE) %>% 
  filter(!is.na(birth_country)) %>% 
  mutate(birth_country = fct_reorder(birth_country, n)) %>% 
  ggplot(aes(decade, n, fill = category))+
  geom_bar(stat = "identity")+
  coord_polar()+
  scale_fill_brewer(palette = "Greens") +
  facet_wrap(~birth_country)

```
### sources: UC Business Analytics R Programming Guide-Parallel coordinate plots(http://uc-r.github.io/gda),                                  Graphical Data Analysis with R by Antony Unwin (http://www.gradaanwr.net/content/ch06/)
```{r}
library(GGally)

winners_summarized <- nobel_winner_all_pubs %>%
  filter(pub_year <= prize_year) %>%
  group_by(laureate_id,
           laureate_name,
           category,
           prize_year,
           prize_decade) %>%
  summarize(papers_before_prize = n(),
            papers_before_prize_5_years = sum(pub_year >= prize_year - 5),
            average_paper_age = mean(prize_year - pub_year),
            winning_paper_age = mean((prize_year - pub_year)[is_prize_winning_paper == "YES"])) %>% 
  ungroup()
```


```{r}
variables <- c("winning_paper_age", "papers_before_prize", "average_paper_age")

winners_summarized %>% 
  select(variables) %>% 
  ggparcoord(alpha = .05, scale = "center")

winners_summarized %>% 
  select(variables) %>% 
  mutate(Above_Avg = winning_paper_age >
           mean(winning_paper_age))%>% 
  ggparcoord(
    alpha = .05,
    scale = "center",
    columns = 1:4,
    groupColumn = "Above_Avg"
    )

#  mutate(pbp = abbreviate(papers_before_prize),
         #pbp5 =abbreviate(papers_before_prize_5_years),
         #apa = abbreviate(average_paper_age),
         #wpa = abbreviate(winning_paper_age))
```
